\documentclass[10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scaled]{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark}
\usepackage{enumitem}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlength{\emergencystretch}{3em}
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, topsep=3pt, parsep=0pt}

\definecolor{textdark}{HTML}{1F2937}
\definecolor{textmuted}{HTML}{4B5563}
\definecolor{rulegray}{HTML}{9CA3AF}
\colorlet{RULEGRAY}{rulegray}

\hypersetup{colorlinks=true, urlcolor={textdark}, linkcolor={textdark}}

\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\color{rulegray}\titlerule]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% Project command
\newcommand{\project}[4]{%
  \textbf{#1} \hfill \textit{#2}\\[-1pt]%
  {\small\textcolor{textmuted}{#3}}%
  #4\par\vspace{5pt}%
}

\begin{document}

% ═══════════════════════════════════════════
%  HEADER — linear layout (ATS-safe)
% ═══════════════════════════════════════════
{\LARGE \textbf{Panthaweekan Somngam}}\\[3pt]
Software Engineer\\[1pt]
Bangkok, Thailand (GMT+7) \quad\textbar\quad Open to Remote / Hybrid\\
\href{mailto:panthaweekansomngam@gmail.com}{panthaweekansomngam@gmail.com} \quad\textbar\quad +66 946359510\\
\href{https://github.com/Panthaweekan}{github.com/Panthaweekan} \quad\textbar\quad \href{https://www.linkedin.com/in/panthaweekan/}{linkedin.com/in/panthaweekan} \quad\textbar\quad \href{https://panthaweekan.github.io/Portfolio/}{panthaweekan.github.io/Portfolio}\\
{\small EN (Intermediate) \textbar{} TH (Native)}

% ═══════════════════════════════════════════
%  PROFESSIONAL EXPERIENCE
% ═══════════════════════════════════════════
\section*{Professional Experience}

\textbf{Associate Software Engineer} \hfill \textit{May 2025 -- Present}\\
SCB TechX, Bangkok, Thailand (Hybrid)
\begin{itemize}
  \item Developed a Go microservice handling token validation, authentication, and request routing for SCB Easy's 10M+ user platform, integrated behind Kong as part of a phased migration away from a legacy on-premise gateway.
  \item Designed the plugin system, routing engine, caching layer, and observability infrastructure for the new gateway, with Prometheus metrics and structured logging ready for production rollout.
  \item Designed and developed an enterprise asset management platform with multi-stage approval workflows, role-based access control for six user roles, financial reporting dashboards, and real-time notifications, used across the organization.
  \item Leveraged AI-assisted development tools across code generation, unit-testing, refactoring, architecture review, and documentation to accelerate delivery on complex features.
\end{itemize}

\textbf{Full Stack Developer (Work-Study Scholarship)} \hfill \textit{2023 -- 2025}\\
Chiang Mai University, Faculty of Engineering, Chiang Mai, Thailand
\begin{itemize}
  \item Designed and deployed two production web applications serving 500+ active users, owning the full lifecycle from stakeholder requirements through containerized deployment.
  \item Developed a real-time room reservation system with role-based access, admin dashboard, and mobile push notifications, adopted by the faculty for daily scheduling.
  \item Developed a multi-stage certificate approval workflow that digitized a paper-based process, reducing turnaround from days to hours.
  \item Applied clean architecture and test-driven development across all projects, building RESTful APIs in Go with React/TypeScript frontends and PostgreSQL.
\end{itemize}

% ═══════════════════════════════════════════
%  PROJECTS
% ═══════════════════════════════════════════
\section*{Projects}

\project
  {API Gateway Microservice \textnormal{\textcolor{textmuted}{--- SCB TechX}}}
  {2025 -- Present}
  {Go, Fiber, PostgreSQL, Redis, Kong, Prometheus, Kubernetes}
  {\begin{itemize}
  \item Built a token service and routing migration layer in Go behind Kong to incrementally replace a legacy gateway, implementing token authentication, plugin-based request transformation, and per-service circuit breaking with retry and exponential backoff across 30+ microservices.
  \item Developed a declarative config sync system based on the Kong decK pattern, using YAML route definitions with diff, rollback, and response caching — enabling GitOps-style config management and safe phased rollouts.
  \item Structured the service using Hexagonal Architecture with strict layer separation, dependency injection, and interface-driven design — keeping core business logic fully testable and decoupled from Kong, Redis, and all infrastructure dependencies.
  \end{itemize}}

\project
  {Inventory Asset Management System \textnormal{\textcolor{textmuted}{--- SCB TechX}}}
  {2025}
  {Ruby on Rails, React, TypeScript, PostgreSQL, Azure AD, Docker}
  {\begin{itemize}
    \item Built a database-driven workflow engine to handle complex request lifecycles across four parallel workflows (request, spare, repair, return), enforcing approval chains per role and step.
    \item Implemented role-based access control for six user roles with Azure AD single sign-on.
    \item Built reporting dashboards aggregating asset requests, utilization, financial summaries, and processing efficiency, with Excel and CSV export.
    \item Developed the frontend with reusable components, type-safe API clients generated from the backend specification, and full offline-capable PWA support with push notifications.
  \end{itemize}}

\newpage

\project
  {SD-Booking --- Room Reservation System \textnormal{\textcolor{textmuted}{--- Chiang Mai University}}}
  {2023 -- 2024}
  {Go, React, TypeScript, PostgreSQL, PWA, Docker}
  {\begin{itemize}
    \item Built a real-time room booking platform serving 500+ faculty users with role-based access, booking conflict detection, and mobile push notifications, adopted for daily operations.
  \end{itemize}}

\project
  {\href{https://github.com/Panthaweekan/silver-octo-palm-tree}{FitJourney --- Fitness Tracking Platform} \textnormal{\textcolor{textmuted}{--- Side Project}}}
  {2026}
  {Next.js, Supabase, Tailwind CSS, OpenAI API, Vercel}
  {\begin{itemize}
    \item Shipped a full-stack fitness PWA addressing a personal gap in daily tracking --- consolidating workout logging, nutrition, body metrics, and AI-powered meal scanning into a single self-hosted tool.
    \item Designed analytics dashboards for performance trends and calorie tracking; architected as a monorepo with Supabase (auth, DB, storage) and Vercel edge deployment for fast cold starts.
  \end{itemize}}

\project
  {\href{https://github.com/Panthaweekan/tts}{Twitch Chat TTS Bot} \textnormal{\textcolor{textmuted}{--- Side Project}}}
  {2026}
  {Bun, Microsoft Edge TTS, tmi.js, FFplay}
  {\begin{itemize}
    \item Engineered a real-time Twitch TTS bot that pipes synthesized audio directly from memory to playback, eliminating disk I/O and reducing per-message overhead versus file-based approaches --- supporting Thai and English neural voices via Microsoft Edge TTS.
    \item Built a message priority queue with anti-spam filtering and automated OAuth token refresh to handle high-volume chat reliably without manual intervention.
  \end{itemize}}

% ═══════════════════════════════════════════
%  EDUCATION
% ═══════════════════════════════════════════
\section*{Education}
\textbf{Bachelor of Engineering in Computer Engineering} \hfill \textit{Graduated 2025}\\
Chiang Mai University \hfill Second-Class Honours\quad GPA: 3.32/4.00\\
{\small Thesis: \textit{LongPlan} --- Study plan validator using graph algorithms (topological sort, cycle detection) and curriculum rule enforcement. Built in Go with React frontend.}

% ═══════════════════════════════════════════
%  SKILLS — plain comma-separated (ATS-safe)
% ═══════════════════════════════════════════
\section*{Skills}

\textbf{Languages:} Go, TypeScript, JavaScript, Ruby, Python, SQL, Java, HTML/CSS, Haskell\\[2pt]
\textbf{Frameworks:} Fiber, Gin, Ruby on Rails, React, Next.js, Node.js, Vite, Tailwind CSS, MUI, TanStack Query\\[2pt]
\textbf{Infrastructure:} PostgreSQL, Redis, Docker, Kubernetes, AWS, Kong API Gateway, CA Layer 7, Nginx, Supabase, Vercel, Linux\\[2pt]
\textbf{Observability:} Prometheus, Grafana, ELK Stack\\[2pt]
\textbf{Tools:} Git, GitHub Actions, Jenkins, HashiCorp Vault\\[2pt]
\textbf{Practices:} System Design, Data Structures \& Algorithms, REST APIs, Microservices, CI/CD, TDD, SOLID, OOP, Agile/Scrum

\end{document}